Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-07-29 analysis/paper/paper.Rmd
resolve merge conflict and adjust the plots

```{r boxplot-size-by-phase}
# size boxplot by period
boxplot_size <-
  ggplot(jpgs_imported_coo_size_pcs_metric,
         aes(Diameter1_Body, fct_rev(y))) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "body diameter (mm)", y = "") +
  scale_y_discrete(breaks = c("Pre-European", "Post-European", "Chinese"),
                   labels = c("Pre-\nEuropean", "Post-\nEuropean", "Chinese")) +
  theme(axis.text = element_text(size = 8)) +
  theme_bw()
```

```{r pcs-size-regression}
# can pc1 predict size by period?
pc1_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc1",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "", y = "PC1") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))

# can pc2 predict size by period?
pc2_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc2",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "body diameter (mm)", y = "PC2") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))
```

```{r size-regression-plot-together}
# plot boxplot and regression together 
right_column <-
  plot_grid(pc1_size_reg, pc2_size_reg, ncol = 1)

size_boxplot_regression <-
  plot_grid(boxplot_size,
            right_column,
            labels = c("A", "B"),
            label_size = 12,
            rel_widths = c(1.8, 3.7))

>>>>

```{r size-analysis-prep-2}
# combine with cv information 
size_pcs_cv_join <-
  jpgs_imported_coo_size_pcs_metric %>% 
  group_by(y) %>% 
  mutate(Diameter1_Body_ave = round(mean(Diameter1_Body), 2),
         cv_body_diameter = round(sd(Diameter1_Body)/mean(Diameter1_Body), 
                                  digits = 2)*100) %>%
  mutate(phase = as.factor(y)) %>% 
  left_join(cv_pcs_all) %>% 
  left_join(pc1_df_with_filename)
  #distinct(phase, cv_pc1, cv_pc2, cv_pc3, Diameter1_Body_ave, cv_body_diameter)
```

```{r boxplot-size-by-phase}
size_cv_df <-
  size_pcs_cv_join %>% 
  distinct(phase, Diameter1_Body_ave, cv_body_diameter, cv_pc1) %>% 
  mutate(cv_body_diameter_label = paste("CV =", cv_body_diameter, "%"),
         Diameter1_Body_ave_label = paste("mean=", Diameter1_Body_ave))

cv_diameter_label <- size_cv_df$cv_body_diameter_label

# size boxplot by period
boxplot_size <-
  ggplot(jpgs_imported_coo_size_pcs_metric,
         aes(Diameter1_Body, fct_rev(y))) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "body diameter\n(mm)", y = "") +
  scale_y_discrete(breaks = c("Pre-European", "Post-European", "Chinese"),
                   labels = c("Pre-\nEuropean", "Post-\nEuropean", "Chinese")) +
  annotate("text", x = c(126,122,144), y = c(2,1,3), 
           size = 2, label = cv_diameter_label) +
  theme_bw() +
  theme(axis.text.x = element_text(size = rel(0.9)),
        axis.text.y = element_text(size = rel(0.9)))
```

```{r boxplot-pc1-ave-size}
library(ggrepel)
y_limits <- c(NA, 32)
boxplot_ave_size_cv_pc <-
  size_cv_df %>% 
  ggplot(aes(cv_body_diameter, cv_pc1)) +
  geom_point() +
  geom_text_repel(label = size_cv_df$phase, 
                  size = 2.5) + 
  labs(x = "CV of body diameter (%)",
       y = "CV of PC1\n(%)") +
  theme(legend.position = "none") +
  theme_bw() +
  theme(axis.text.x = element_text(size = rel(0.9)),
        axis.text.y = element_text(size = rel(0.9)))
```

label = size_cv_df$phase,
                   size = 2.5, ylim = y_limits

```{r pcs-size-regression}
# can pc1 predict size by period?
pc1_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc1",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "", y = "PC1") +
    theme(axis.text = element_text(size = 8)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))

# can pc2 predict size by period?
pc2_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc2",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "body diameter (mm)", y = "PC2") +
    theme(axis.text = element_text(size = 8)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))
```

```{r size-regression-plot-together}
# plot boxplot and regression together 
left_column <-
  plot_grid(boxplot_size, boxplot_ave_size_cv_pc, 
            ncol = 1, rel_heights = c(1.1,1), 
            labels = c("A", "B"), label_size = 12 )

right_column <-
  plot_grid(pc1_size_reg, pc2_size_reg, ncol = 1)

size_boxplot_regression <-
  plot_grid(left_column,
            right_column,
            labels = c("", "C", "B"),
            label_size = 12,
            rel_widths = c(1.8, 3.7))
